---
author: "Prashant Kalvapalle"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document:
    theme: flatly
    toc: TRUE
    toc_float: TRUE
---

---
title: `r title_name`
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 12, fig.height = 4)

```

## Goal of the analysis

Visualizing SARS CoV2-N1,N2 (multiplexed), pepper mild mottle virus (pMMoV) and BCoV surrogate spiked into wastewater samples

```{r scripts, fig.width = 12}

# Make a string to filter out all regular WWTP and manhole samples to plot separately
wwtp_manhole_names <- str_c(WWTP_symbols_regex, manhole_symbols_regex, sep = '|')


# Return TRUE if percentage recovery data is present
show_percent_recovery <- 
  presentable_data %>% 
  filter(!is.na(Percentage_recovery_BCoV)) %>% 
  {!plyr::empty(.)}

# Return TRUE of pMMoV is a listed Target in the data
show_pMMoV <- 'pMMoV' %in% presentable_data$Target_Name


# plot individual biological replicates (for quality control)
# map2(list_rawqpcr, read_these_sheets, ~(plot_biological_replicates(.x, title_text = .y)))

```


## Plots (WWTP labels)

### (copies per l WW)

```{r all_plot}
# all the plotting functions plot data: "long_processed_minimal" by default

  concWW_plot <- 
  plot_mean_sd_jitter(WWTP_filtering_var = wwtp_manhole_names, 
                      x_var = WWTP, y_var = Copies_Per_Liter_WW, 
                      ylabel = 'Genome copies/l Wastewater') 
  
  concWW_plot %>% format_logscale_y() %>% print()
  
```


### (copies per ul RNA)

```{r copiesrna}

  concWW_plot <- plot_mean_sd_jitter(x_var = WWTP, y_var = Copies_per_uL_RNA, 
                                     ylabel = 'Genome copies/ul RNA') 
  
  concWW_plot %>% format_logscale_y() %>% print()
  
```


## Surrogate viruses

```{r summarizing_plot}

plot_mean_sd_jitter(target_filter_var = 'BCoV|BRSV|pMMoV', 
                    x_var = WWTP, ylabel = 'Genome copies/l Wastewater') %>%  
  format_logscale_y() %>% 
  print()

# old stuff -- not used since BCoV is not being done much..
# open circles : Copies of surrogate virus spiked in
# filled circles : Copies of surrogate virus recovered


```

`r  if(show_percent_recovery) {"### Percentage viral RNA recovery"}`

```{r percentreco}

if(show_percent_recovery) {
  percentreco_plt <- 
    plot_mean_sd_jitter(target_filter_var = 'BCoV|BRSV', 
                        x_var = WWTP, y_var = Percentage_recovery_BCoV,
                        ylabel = 'Percentage recovery of surrogate virus') 
  
  percentreco_plt %>% print()
  
  # same plot in logscale y axis  
  percentreco_plt %>% format_logscale_y() %>% print()
}
  
```

## Controls and additional samples

```{r controls_recos, fig.width= 6}

extra_samples_to_plot <- str_c('Std|Control', '|Vaccine|NTC') %>% str_remove('\\|Std|Std\\|')

# N1/N2 and BCoV plots : Copies/ul RNA
plot_mean_sd_jitter(WWTP_filtering_var = wwtp_manhole_names, exclude_WWTP = T, x_var = WWTP) %>% format_logscale_y() %>% print()


# Copies/l WW: N1/N2 and BCoV plots
plot_mean_sd_jitter(WWTP_filtering_var = wwtp_manhole_names, exclude_WWTP = T, 
                    x_var = WWTP, y_var = Copies_Per_Liter_WW,
                    ylabel = 'Genome copies/l Wastewater') %>% 
  
  format_logscale_y() %>% print()

# # recovered vs spiked in plot for extra samples
# plot_mean_sd_jitter(long_vol_qpcr_summary, long_vol_qpcr_raw, long_format = T, measure_var = 'Recovered', Sample_filtering_var = extra_samples_to_plot, exclude_sample = F, x_var = WWTP, ylabel = 'Genome copies/l Wastewater') %>%
#   format_logscale_y() %>% print()

# % plot for extra samples
plot_mean_sd_jitter(measure_var = 'Percentage_recovery_BCoV', WWTP_filtering_var = wwtp_manhole_names, exclude_WWTP = T, target_filter_var= 'BCoV|BRSV', x_var = WWTP, ylabel = 'Percentage recovery of surrogate virus') %>% print()

```


## Scatter plots

### N1 vs N2 replicate

```{r n1n2}

# NOTE: This function is very useful - errors here indicate that there are overlapping labels in the data: Check the sample naming sheet first thing

plot_scatter(processed_quant_data) %>% print()

```

### N1 vs N2 logscale

```{r n1n2avg}

plot_scatter(processed_quant_data, x_var = N1_multiplex, y_var = N2_multiplex) %>% 
  format_logscale_x() %>% 
  format_logscale_y() %>% 
  print()

```

### BCoV vs N2 avg

```{r n2bcov}

 plot_scatter(processed_quant_data, x_var = BCoV) %>% print()

```

## Ordered plots

### (copies/l WW)

```{r n1n2streamlined}

ordered_plt1 <- plot_mean_sd_jitter(x_var = WWTP, ascending_order = TRUE, ylabel = 'Genome copies/l Wastewater')

ordered_plt1 %>% format_logscale_y() %>% print()

```

### (copies/ul RNA)

```{r orderedrna}

ordered_plt_rna <- 
  plot_mean_sd_jitter(x_var = WWTP, y_var = Copies_per_uL_RNA,
                      ascending_order = T, ylabel = 'Genome copies/ul RNA')

ordered_plt_rna %>% format_logscale_y() %>% print()

```


`r if(show_percent_recovery) {"### Percentage recovery"}`

```{r percentRecoverystreamlined}

if(show_percent_recovery) {
  recostr_plot <- 
    plot_mean_sd_jitter(x_var = Percentage_recovery_BCoV, ascending_order = T,
                        ylabel = 'Percentage recovery of surrogate')
}

```

