---
title: "Weekly comparisons"
author: "Prashant Kalvapalle"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document:
    theme: flatly
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10, fig.height = 4)

# Return TRUE if percentage recovery data is present
show_percent_recovery <- 
  results_abs %>% 
  filter(!is.na(Percentage_recovery_BCoV)) %>% 
  {!plyr::empty(.)}

# Return TRUE of BCoV is a listed Target in the data
show_BCoV <- 'BCoV' %in% results_abs$Target_Name

# Return TRUE of pMMoV is a listed Target in the data
show_pMMoV <- 'pMMoV' %in% results_abs$Target_Name
  
```

`r if(show_percent_recovery){"## Percentage Recovery \n ### Density plot | Recovery "}`

```{r}

if(show_percent_recovery) {
  results_abs %>% 
    filter(!is.na(Percentage_recovery_BCoV)) %>% 
    ggplot(aes(x = Week, y = Percentage_recovery_BCoV)) + geom_jitter(width = .1)
}

```

`r  if(show_percent_recovery) {"### Violin + Density plot | Recovery"}`

```{r}

if(show_percent_recovery) {
  results_abs %>% 
    filter(!is.na(Percentage_recovery_BCoV)) %>% 
    ggplot(aes(x = Week, y = Percentage_recovery_BCoV)) + 
    geom_violin(show.legend = F) + 
    geom_jitter(width = .1, alpha = .2)
}

```

`r  if(show_percent_recovery) {"### Dot plot | Recovery"}`


```{r dots}

if(show_percent_recovery) {
  nameless <- results_abs %>% select(Week, Percentage_recovery_BCoV) %>% drop_na() %>% group_by(Week) %>% arrange(Percentage_recovery_BCoV) %>%  mutate(id = row_number()) 
  
  nameless %>% ggplot(aes(x = id, y = Percentage_recovery_BCoV, colour = Week)) + geom_point() + geom_line()
}

```

## Copies/L | Density plots

### Copies/L 

```{r allviolin}

den.plt <- 
{results_abs %>% 
  ggplot(aes(x = Week, y = Copies_Per_Liter_WW, colour = Target_Name)) + 
  geom_jitter(width = .1) + 
  geom_violin(show.legend = F)} %>% 
  print()

ggplotly(den.plt, tooltip = 'label')

```

### Log Copies/L

```{r logallviolin}

den.plt %>% format_logscale_y() %>% print() %>% 
  ggplotly(tooltip = 'label')

```

### N1-N2 Copies/L

```{r n12violin}

den.plt_N12 <- results_abs %>% filter(str_detect(Target_Name, 'N1|N2')) %>% 
  ggplot(aes(x = Week, y = Copies_Per_Liter_WW, colour = Target_Name, label = WWTP)) + geom_jitter(width = .1) + geom_violin(show.legend = F)

print(den.plt_N12)

ggplotly(den.plt_N12, tooltip = 'label')

```

### Logscale N1-N2 Copies/L

```{r logn12violin}

den.plt_N12 %>% format_logscale_y() %>% print()

```


`r if(show_pMMoV) {"### pMMoV Copies/L"}`

```{r pmmoviolin}

den.plt_pmmov <- results_abs %>% filter(str_detect(Target_Name, 'pMMoV')) %>% 
  ggplot(aes(x = Week, y = Copies_Per_Liter_WW, colour = Target_Name, label = WWTP)) + geom_jitter(width = .1) #+ geom_violin(show.legend = F)

print(den.plt_pmmov)

ggplotly(den.plt_pmmov, tooltip = 'label')

```


`r if(show_pMMoV) {"### Logscale pMMoV Copies/L"}`

```{r logpmmovviolin}

den.plt_pmmov %>% format_logscale_y() %>% print()

```


## Scatter plots (correlations)

### N comparisions | Scatter

```{r}

Copies_Per_Liter_WW_wide <- results_abs %>% select(WWTP, Target_Name, Week, Copies_Per_Liter_WW) %>% group_by(Week, Target_Name, WWTP) %>% mutate(id = row_number()) %>% unite('WWTP', c('WWTP', id)) %>% pivot_wider(names_from = Target_Name, values_from = Copies_Per_Liter_WW) 

plt.sctrN <- Copies_Per_Liter_WW_wide %>% ggplot(aes(x = `SARS CoV-2 N1`, y = `SARS CoV-2 N2`, colour = Week)) + geom_point() + geom_smooth(method = 'lm') 

print(plt.sctrN)

```

Interactive plot

```{r}
plt.sctrN %>% ggplotly(dynamicTicks = T)

```

### N1 vs BCoV | Scatter

```{r}

Copies_Per_Liter_WW_wide <- results_abs %>% 
  
  select(WWTP, Target_Name, Week, Copies_Per_Liter_WW) %>% 
  group_by(Week, Target_Name, WWTP) %>% 
  
  mutate(id = row_number()) %>% 
  unite('WWTP', c('WWTP', id)) %>% 
  
  pivot_wider(names_from = Target_Name, values_from = Copies_Per_Liter_WW) 

if('BCoV_M' %in% colnames(Copies_Per_Liter_WW_wide)) {
  plt.sctrNBCOV <- Copies_Per_Liter_WW_wide %>% 
    ggplot(aes(x = `SARS CoV-2 N1`, y = `BCoV_M`, colour = Week)) + 
    geom_point() + 
    geom_smooth(method = 'lm') 
  
  print(plt.sctrNBCOV)
}


```


### N1 vs pMMoV | Scatter

```{r}

if('pMMoV' %in% colnames(Copies_Per_Liter_WW_wide)) {
  plt.sctrNpMMoV <- Copies_Per_Liter_WW_wide %>% 
    ggplot(aes(x = `SARS CoV-2 N1`, y = pMMoV, colour = Week)) + 
    geom_point() + 
    geom_smooth(method = 'lm') 
  
  print(plt.sctrNpMMoV)
}

```

### Interactive plots

```{r}

if('BCoV_M' %in% colnames(Copies_Per_Liter_WW_wide)) {
  plt.sctrNBCOV %>% ggplotly(dynamicTicks = T)
}

if('pMMoV' %in% colnames(Copies_Per_Liter_WW_wide)) {
  plt.sctrNpMMoV %>% ggplotly(dynamicTicks = T)
}


```


## Timeseries across site

### Copies/L | Timeseries

```{r timeseries, fig.width= 16, fig.height= 12}

plt_timeseries_all_targets <- 
  plot_mean_sd_jitter(results_abs,
                      sample_filtering_var = extra_categories, exclude_sample = T, 
                      x_var = Week, y_var = Copies_Per_Liter_WW, colour_var = Target_Name, 
                      ylabel = 'Genome copies/l Wastewater') + 
  geom_line(aes(group = Target_Name)) +
  facet_wrap(facets = ~WWTP, scales = 'free_x')

```

#### Logscale Copies/L | Timeseries

```{r timeserieslog, fig.width= 16, fig.height= 12}

plt_timeseries_all_targets  %>% 
  format_logscale_y() %>% 
  print()

```

### N1/N2 Copies/L | Timeseries

```{r timeseriesN, fig.width= 16, fig.height= 12}

plt_timeseries_N12 <- 
  plot_mean_sd_jitter(results_abs,
                      sample_filtering_var = extra_categories, exclude_sample = T,
                      target_filter_var = 'N1|N2',
                      x_var = Week, y_var = Copies_Per_Liter_WW, colour_var = Target_Name, 
                      ylabel = 'Genome copies/l Wastewater') + 
  geom_line(aes(group = Target_Name)) +
  facet_wrap(facets = ~WWTP, scales = 'free_x')

```

### Logscale N1/N2 Copies/L | Timeseries

```{r logtimeseriesN, fig.width= 16, fig.height= 12}

plt_timeseries_N12 %>% format_logscale_y() %>% print()

```


`r if(show_BCoV) {"### BCoV | Timeseries"}`
 
```{r timeseriesbcov, fig.width= 16, fig.height= 12}
# if('BCoV' %in% colnames(results_abs)) {
plt_timeseries_BCoV <- 
  plot_mean_sd_jitter(results_abs,
                      sample_filtering_var = extra_categories, exclude_sample = T,
                      target_filter_var = 'BCoV',
                      x_var = Week, y_var = Copies_Per_Liter_WW, colour_var = Target_Name, 
                      ylabel = 'Genome copies/l Wastewater') + 
  geom_line(aes(group = Target_Name)) +
  facet_wrap(facets = ~WWTP, scales = 'free_x')
# }

```


`r if(show_percent_recovery) {"### Percentage recovery | Timeseries"}`

```{r timeseriespercentreco, fig.width= 16, fig.height= 12}

if(show_percent_recovery){
  plt_timeseries_percent.recovery <- 
    plot_mean_sd_jitter(results_abs,
                        sample_filtering_var = extra_categories, exclude_sample = T,
                        target_filter_var = 'BCoV',
                        x_var = Week, y_var = Percentage_recovery_BCoV, colour_var = Target_Name, 
                        ylabel = 'Percentage of BCoV copies recovered') + 
    geom_line(aes(group = Target_Name)) +
    facet_wrap(facets = ~WWTP, scales = 'free_x')
}

```

<!-- This code is obsolete since population, flow rate is no longer retrievable - 16-11-2021; PK -->
<!-- ### Copies/person timeseries -->

<!-- ```{r normalizedcopiesn, fig.width= 16, fig.height= 12} -->

<!-- summary_normalized <- results_abs %>% select(Facility, WWTP, Target_Name, Copies_per_uL_RNA: Percentage_recovery_BCoV, Week, `Viral load per capita per day`, -any_of('Bottle')) %>% -->
<!--   mutate('Sample_name' = Week) %>%  -->
<!--   group_by(`Sample_name`, Target_Name, Facility, WWTP, Week) %>%  -->
<!--   summarise_at(c('Viral load per capita per day'), lst(mean, sd), na.rm = T) -->

<!-- normalized_copies_N12 <- list(summary_normalized, results_abs.list$raw.dat) %>% map(filter, str_detect(Target_Name, 'N1|N2')) %>% setNames(c('summ.dat', 'raw.dat')) -->

<!-- plt_week4 <- plot_mean_sd_jitter(normalized_copies_N12, long_format = F, sample_var = extra_categories, exclude_sample = T, x_var = Week, y_var = `Viral load per capita per day`, facet_var = WWTP, colour_var = Target_Name, ylabel = 'Viral load per capita per day', facet_style = 'manual') + geom_line(aes(group = Target_Name)) + facet_wrap(facets = ~WWTP, scales = 'free_x') -->

<!-- plt_week4 %>% print() -->

<!-- plt_week4 %>% format_logscale_y() %>% print() -->

<!-- ``` -->
