---
title: "Weekly comparisons"
author: "Prashant Kalvapalle"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document:
    theme: flatly
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = F, message = F, warning = F, fig.width = 10, fig.height = 4)
```

## Percentage Recovery 

### Recovery | Density plot

```{r}

results_abs %>% ggplot(aes(x = Week, y = `Percentage_recovery_BCoV`)) + geom_jitter(width = .1)
```

### Recovery | Violin + Density plot

```{r}

results_abs %>% ggplot(aes(x = Week, y = `Percentage_recovery_BCoV`)) + geom_violin() + geom_jitter(width = .1, alpha = .2)
```

### Recovery | Dot plot

```{r dots}

nameless <- results_abs %>% select(Week, `Percentage_recovery_BCoV`) %>% drop_na() %>% group_by(Week) %>% arrange(`Percentage_recovery_BCoV`) %>%  mutate(id = row_number()) 

nameless %>% ggplot(aes(x = id, y = `Percentage_recovery_BCoV`, colour = Week)) + geom_point() + geom_line()
```

## Copies/L | Density plots

### Copies/L | Violin + Density plot

```{r allviolin}

results_abs %>% 
  ggplot(aes(x = Week, y = `Copies/l WW`, colour = Target)) + geom_jitter(width = .1) + geom_violin()
```

### N1-N2 Copies/L | Violin + Density plot

```{r n12violin}

den.plt <- results_abs %>% filter(str_detect(Target, 'N1|N2')) %>% 
  ggplot(aes(x = Week, y = `Copies/l WW`, colour = Target, label = WWTP)) + geom_jitter(width = .1) + geom_violin()

print(den.plt)

ggplotly(den.plt, tooltip = 'label')
```

### Logscale N1-N2 Copies/L | Violin + Density plot

```{r logn12violin}

den.plt %>% format_logscale_y() %>% print()
```

## Scatter plots (correlations)

## N comparisions | Scatter

```{r}

results_wide <- results_abs %>% select(WWTP, Target, Week, `Copies/l WW`) %>% group_by(Week, Target, WWTP) %>% mutate(id = row_number()) %>% unite('WWTP', c('WWTP', id)) %>% pivot_wider(names_from = Target, values_from = `Copies/l WW`) 

plt.sctrN <- results_wide %>% ggplot(aes(x = `SARS CoV-2 N1`, y = `SARS CoV-2 N2`, colour = Week)) + geom_point() + geom_smooth(method = 'lm') 

print(plt.sctrN)

```

Interactive plot

```{r}
plt.sctrN %>% ggplotly(dynamicTicks = T)

```

## N1 vs BCoV | Scatter

```{r}

results_wide <- results_abs %>% select(WWTP, Target, Week, `Copies/l WW`) %>% group_by(Week, Target, WWTP) %>% mutate(id = row_number()) %>% unite('WWTP', c('WWTP', id)) %>% pivot_wider(names_from = Target, values_from = `Copies/l WW`) 

plt.sctrNBCOV <- results_wide %>% ggplot(aes(x = `SARS CoV-2 N1`, y = `BCoV_M`, colour = Week)) + geom_point() + geom_smooth(method = 'lm') 

print(plt.sctrNBCOV)

```

Interactive plot

```{r}
plt.sctrNBCOV %>% ggplotly(dynamicTicks = T)

```


## Timeseries across weeks

### Weekly timeseries - N1/N2/BcoV

```{r timeseries, fig.width= 16, fig.height= 12}

# Make mean of biological replicates
results_abs.list <- list(
  raw.dat = results_abs %>% mutate('Sample_name' = Week), # dummy column - for compatibility with plot_mean_sd_jitter() function

  summ.dat = results_abs %>% select(Facility, WWTP, Target, `Copies/ul RNA`: `Percentage_recovery_BCoV`, Week, -any_of('Bottle')) %>%
  group_by(Target, Facility, WWTP, Week) %>% summarise_at(c('Copies/l WW'), lst(mean, sd), na.rm = T) %>% 
    mutate('Sample_name' = Week)
)

plt_week1 <- plot_mean_sd_jitter(results_abs.list, long_format = F, sample_var = extra_categories, exclude_sample = T, x_var = Week, y_var = `Copies/l WW`, colour_var = Target, ylabel = 'Genome copies/l Wastewater') + geom_line(aes(group = Target)) +
  facet_wrap(facets = ~WWTP, scales = 'free_x')

plt_week1 %>% print()
```


### Weekly timeseries - N1/N2 

```{r timeseriesN, fig.width= 16, fig.height= 12}
only_N12 <- results_abs.list %>% map(filter, str_detect(Target, 'N1|N2'))

plt_week2 <- plot_mean_sd_jitter(only_N12, long_format = F, sample_var = extra_categories, exclude_sample = T, x_var = Week, y_var = `Copies/l WW`, colour_var = Target, ylabel = 'Genome copies/l Wastewater') + geom_line(aes(group = Target)) +
  facet_wrap(facets = ~WWTP, scales = 'free_x')

plt_week2 %>% print()
```

### Logscale timeseries - N1/N2 

```{r logtimeseriesN, fig.width= 16, fig.height= 12}

plt_week2 %>% format_logscale_y() %>% print()
```

### Weekly timeseries - BCoV 

```{r timeseriesbcov, fig.width= 16, fig.height= 12}
only_bcov <- results_abs.list %>% map(filter, str_detect(Target, 'BCoV'))

plt_week3 <- plot_mean_sd_jitter(only_bcov, long_format = F, sample_var = extra_categories, exclude_sample = T, x_var = Week, y_var = `Copies/l WW`, colour_var = Target, ylabel = 'Genome copies/l Wastewater') + geom_line(aes(group = Target)) +
  facet_wrap(facets = ~WWTP, scales = 'free_x')

plt_week3 %>% print()
```

### Weekly timeseries - Percentage recovery 

```{r timeseriespercentreco, fig.width= 16, fig.height= 12}

summary_reco <- results_abs %>% select(Facility, WWTP, Target, `Copies/ul RNA`: `Percentage_recovery_BCoV`, Week, -any_of('Bottle')) %>%
  mutate('Sample_name' = Week) %>% 
  group_by(`Sample_name`, Target, Facility, WWTP, Week) %>% 
  summarise_at(c('Percentage_recovery_BCoV'), lst(mean, sd), na.rm = T)

recovery_data.list <- list(summary_reco, results_abs.list$raw.dat) %>% map(filter, str_detect(Target, 'BCoV')) %>% setNames(c('summ.dat', 'raw.dat'))

plt_week3 <- plot_mean_sd_jitter(recovery_data.list, long_format = F, sample_var = extra_categories, exclude_sample = T, x_var = Week, y_var = `Percentage_recovery_BCoV`, colour_var = Target, ylabel = 'Percentage of BCoV copies recovered') + geom_line(aes(group = Target)) + facet_wrap(facets = ~WWTP, scales = 'free_x')

plt_week3 %>% print()
```

### Copies/person timeseries

```{r normalizedcopiesn, fig.width= 16, fig.height= 12}

summary_normalized <- results_abs %>% select(Facility, WWTP, Target, `Copies/ul RNA`: `Percentage_recovery_BCoV`, Week, `Viral load per capita per day`, -any_of('Bottle')) %>%
  mutate('Sample_name' = Week) %>% 
  group_by(`Sample_name`, Target, Facility, WWTP, Week) %>% 
  summarise_at(c('Viral load per capita per day'), lst(mean, sd), na.rm = T)

normalized_copies_N12 <- list(summary_normalized, results_abs.list$raw.dat) %>% map(filter, str_detect(Target, 'N1|N2')) %>% setNames(c('summ.dat', 'raw.dat'))

plt_week4 <- plot_mean_sd_jitter(normalized_copies_N12, long_format = F, sample_var = extra_categories, exclude_sample = T, x_var = Week, y_var = `Viral load per capita per day`, facet_var = WWTP, colour_var = Target, ylabel = 'Viral load per capita per day', facet_style = 'manual') + geom_line(aes(group = Target)) + facet_wrap(facets = ~WWTP, scales = 'free_x')

plt_week4 %>% print()

plt_week4 %>% format_logscale_y() %>% print()

```
